---
title: "My analysis"
author: "Hugo Kim"
date: "4/8/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DESeq2)
library(dplyr)
library(Seurat)
library(kableExtra)
library(ggplot2)
library(rhdf5)
```

## Insert mydata

Download my old table (Skip if already Combined)
```{r}
MyRNAseqDataRNB2=read.table("CombinedRNB2Limited100.txt")
Mylabels=mainnames=read.table('listcntRNB2.txt',header=TRUE)
rownames(MyRNAseqDataRNB2)=MyRNAseqDataRNB2[,1]
MyRNAseqDataRNB2=MyRNAseqDataRNB2[,-1]
colnames(MyRNAseqDataRNB2)=Mylabels[,1]
samplematrix2=as.matrix(MyRNAseqDataRNB2)
refs2= read.table("PhenotypeRNB2.txt",header=TRUE)
rownames(refs2)=refs2[,1]
MyRNAseqDataRNB1=read.table("CombinedRNB1Limited100.txt",header=TRUE)
rownames(MyRNAseqDataRNB1)=MyRNAseqDataRNB1[,1]
MyRNAseqDataRNB1=MyRNAseqDataRNB1[,-1]
MyRNAseqDataRNB1=MyRNAseqDataRNB1[match(rownames(MyRNAseqDataRNB2),rownames(MyRNAseqDataRNB1)),]
samplematrix1=as.matrix(MyRNAseqDataRNB1)
refs1= read.table("PhenotypeRNB1.txt",header=TRUE)
rownames(refs1)=refs1[,1]
refsall=rbind(refs2,refs1)
MyRNAseqDataRNBall=cbind(MyRNAseqDataRNB2,MyRNAseqDataRNB1)
samplematrixall=as.matrix(MyRNAseqDataRNBall)
```
IFcombined, use

```{r}
MyRNAseqDataRNB2=read.table("CombinedRNB12.txt")
Mylabels=mainnames=read.table('listcntRNB2_Unlimited.txt',header=TRUE)
rownames(MyRNAseqDataRNB2)=MyRNAseqDataRNB2[,1]
MyRNAseqDataRNB2=MyRNAseqDataRNB2[,-1]
colnames(MyRNAseqDataRNB2)=Mylabels[,1]
samplematrix2=as.matrix(MyRNAseqDataRNB2)
refs2= read.table("PhenotypeRNB12.txt",header=TRUE)
rownames(refs2)=refs2[,1]
refs2=refs2[match(colnames(samplematrixall),rownames(refs2)),]
refsall=refs2
MyRNAseqDataRNBall=MyRNAseqDataRNB2
samplematrixall=as.matrix(MyRNAseqDataRNBall)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
samplematrix=samplematrixall+1
refs=refsall


dds <- DESeqDataSetFromMatrix(countData = samplematrix,
                              colData = refs,
                              design= ~ Regen)
dds <- DESeq(dds)
resultsNames(dds) # lists the coefficients
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
restest <- results(dds, name="Regen_Ref_vs_NO")
write.table(restest,"RNB1&2_Test_DEseq2_Unlimited.txt")
# or to shrink log fold changes association with condition:
res <- results(dds, name="Regen_YES_vs_NO")
write.table(res,"RNB1&2_DEseq2_Unlimited.txt")
```

Lets check which direction is positive
```{r}
Firstgene=t(MyRNAseqData[match("ENSMUSG00000006356.10",rownames(MyRNAseqDataRNB2)),])
```


Ok. now we know "YES" is negative. Lets use biomart to convert ensemble id
```{r}
library(biomaRt)
ensembl <- useEnsembl(biomart = "genes", dataset = "mmusculus_gene_ensembl")
#listEnsembl()
MyensembleGenes_orig=rownames(MyRNAseqDataRNBall)
MyensembleGenes <- sapply(strsplit(MyensembleGenes_orig,"\\."), function(x) x[1])
HUGOID = getBM(attributes = c('ensembl_gene_id', 'external_gene_name'), 
              #filters = 'ensembl_gene_id', 
              values = MyensembleGenes, 
              mart = ensembl)
Mygenescombined=cbind(MyensembleGenes_orig,MyensembleGenes)
HUGOIDMATCHING=HUGOID[match(Mygenescombined[,2],HUGOID[,1]),]
Mygenescombined=cbind(Mygenescombined,HUGOIDMATCHING)
res <- results(dds, name="Regen_YES_vs_NO")
res=cbind(res,Mygenescombined)
write.table(res,"RNB1&2_DEseq2_Unlimited.txt")
```

Lets do same to the diff genes
```{r}
#resfinal=cbind(res,Mygenescombined[,4])
#write.table(resfinal,'RNB1&2_DESEQ.txt')
plot(resfinal$log2FoldChange,-log(resfinal$padj),log=c("y","x"))
```

Lets generate heatmap
``` {r}
#Sort
Hugosdata=MyRNAseqDataRNBall
res.ordered=res[order(res$padj, decreasing = FALSE, na.last = TRUE, method = c("auto")),] #"shell", "quick", "radix"
res.orderedFirst20=res.ordered[1:20,]
res.orderedFirst200=res.ordered[1:200,]
res.ordered$padj[is.na(res.ordered$padj)]<-1
res.orderedAllsignificant=res.ordered[res.ordered$padj<0.05,]
res.orderedFirst200_Neg=res.orderedFirst200[order(res.orderedFirst200$log2FoldChange, decreasing = FALSE, na.last = TRUE, method = c("auto")),]
res.orderedAllsignificant_Neg=res.orderedAllsignificant[order(res.orderedAllsignificant$log2FoldChange, decreasing = FALSE, na.last = TRUE, method = c("auto")),]
GeneofInterest=rownames(res.orderedAllsignificant_Neg)
HugosdataWithFirstDEgenes=Hugosdata[match(GeneofInterest,rownames(Hugosdata)),]
HugosdataWithFirstDEgenesMatrix=as.matrix(HugosdataWithFirstDEgenes)
heatmap(HugosdataWithFirstDEgenesMatrix)
RegenSamples=refsall[refsall$Regen=="YES",]
NoRegenSamples=refsall[refsall$Regen=="NO",]
RegenDE=as.matrix(HugosdataWithFirstDEgenes[,match(rownames(RegenSamples),names(HugosdataWithFirstDEgenes))])
heatmap(RegenDE)

NoRegenDE=as.matrix(HugosdataWithFirstDEgenes[,match(rownames(NoRegenSamples),names(HugosdataWithFirstDEgenes))])
heatmap(NoRegenDE)

#Negatives
mean(RegenDE[1,])
mean(NoRegenDE[1,])

#Positives
mean(RegenDE[nrow(RegenDE),])
mean(NoRegenDE[nrow(NoRegenDE),])

#Average Heatmap
REG=apply(RegenDE,1,function(x) mean(x))
NO=apply(NoRegenDE,1,function(x) mean(x))
All.ave=as.matrix(cbind(REG,NO))
heatmap(All.ave)

```

Lets remove genes with high standard deviation 
```{r}
RegenSTD=apply(RegenDE,1,function(x) sd(x))
RegenSTD_Threshold=mean(RegenSTD)
NoRegenSTD=apply(NoRegenDE,1,function(x) sd(x))
NoRegenSTD_Threshold=mean(NoRegenSTD)

RegenSTD_NoNoRegenGene=RegenSTD[NoRegenSTD<NoRegenSTD_Threshold]
RegenSTD_FINAL=RegenSTD_NoNoRegenGene[RegenSTD_NoNoRegenGene<RegenSTD_Threshold]

NoRegenSTD_NoRegenGene=NoRegenSTD[RegenSTD<RegenSTD_Threshold]
NoRegenSTD_FINAL=NoRegenSTD_NoRegenGene[NoRegenSTD_NoRegenGene<NoRegenSTD_Threshold]

RegenDE_GoodSTD=RegenDE[match(names(RegenSTD_FINAL),rownames(RegenDE)),]
heatmap(RegenDE_GoodSTD)
NoRegenDE_GoodSTD=NoRegenDE[match(names(NoRegenSTD_FINAL),rownames(NoRegenDE)),]
heatmap(NoRegenDE_GoodSTD)
res.orderedAllsignificant_GoodSTD=res.orderedAllsignificant[match(names(RegenSTD_FINAL),rownames(res.orderedAllsignificant)),]
FINALExpression=All.ave[(match(names(RegenSTD_FINAL),rownames(All.ave))),]
heatmap(FINALExpression)
#Lets change
GeneofInterest=Mygenescombined[match(rownames(FINALExpression),Mygenescombined[,1]),4]
#GeneofInterest
namestosave=rownames(FINALExpression)[is.na(GeneofInterest)]
write.table(namestosave,"ENSEMBLEFIND.txt")

```
Make sure to get gene names and have second row to be the gene names(also make sure to make header)

```{r}
FoundGenenames=read.table("ENSEMBLEFIND.txt",header=TRUE)
GeneofInterest[which(is.na(GeneofInterest))]=FoundGenenames[,2]
FINALExpression_Genes=FINALExpression
rownames(FINALExpression_Genes)=GeneofInterest
heatmap(FINALExpression_Genes)
```


Ok Lets Try Seurat Method

```{r}

Hugosdata=MyRNAseqDataRNBall
#Hugosdata=Hugosdata[match(rownames(FINALExpression),rownames(Hugosdata)),]
HugosMeta=refsall
#Remove sample with 0 read

Hugosdata<-Hugosdata[-match("__alignment_not_unique",rownames(Hugosdata)),]
Hugosdata<-Hugosdata[-match("__ambiguous",rownames(Hugosdata)),]
Hugosdata<-Hugosdata[-match("__no_feature",rownames(Hugosdata)),]
Hugosdata<-Hugosdata[-match("__not_aligned",rownames(Hugosdata)),]
Hugosdata<-Hugosdata[-match("__too_low_aQual",rownames(Hugosdata)),]

#HugosMeta=HugosMeta[-124,]


OriginalIdentity=HugosMeta[match(colnames(Hugosdata),HugosMeta[,1]),2]
Batch=HugosMeta[match(colnames(Hugosdata),HugosMeta[,1]),3]
AnimalNumber=HugosMeta[match(colnames(Hugosdata),HugosMeta[,1]),4]
#colnames(Hugosdata)=paste("PATCHseq-",colnames(Hugosdata))

HugosDataObject=CreateSeuratObject(counts=Hugosdata)
HugosDataObject$orig.ident=OriginalIdentity
HugosDataObject$Batch=Batch
HugosDataObject$AnimalNum=AnimalNumber
HugosDataObject[["Percent"]]<-PercentageFeatureSet(HugosDataObject, pattern = "^MT-")
experiment.aggregate<-HugosDataObject
slotNames(experiment.aggregate)
```


## Some basic QA/QC of the metadata, print tables of the 5% quantiles.

Show 5% quantiles for number of genes per cell per sample
```{r quantiles_1, warning=FALSE,error=FALSE,message=FALSE}
kable(do.call("cbind", tapply(experiment.aggregate$nFeature_RNA, 
                      Idents(experiment.aggregate),quantile,probs=seq(0,1,0.05))),
      caption = "5% Quantiles of Genes/Cell by Sample") %>% kable_styling()
```